Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-06-17 main.Rmd
change color for tsibble and gravitas data structure

\noindent All cyclic granularities can be expressed in terms of the index set, and hence, we introduce the data structure in Figure \@ref(fig:data-structure). This basic structure of a tsibble (index, key, measurements) is augmented by columns of cyclic granularities.\todo[inline]{think your diagram should color what's tsibble differently from what's augmented} The total number of cyclic granularities would be based on the number of linear granularities considered in the hierarchy table and presence of any aperiodic cyclic granularities, for example, if we have $n$ periodic linear granularities in the hierarchy table, $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed. Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that could originate from $N_L$ periodic and aperiodic linear granularities. Any attempt to encode all or many of these cyclic granularities at the same time to develop insights on periodicity might fail or otherwise become too numerous for comprehensive human consumption. Instead, this big problem is broken down by focusing on pair of cyclic granularities ($C_i$, $C_j$) at a time for $i, j \in \{1, 2, \dots, N_C\}$. Data sets of the form <$C_i$, $C_j$, $v$> then forms the basis for exploration and analysis of the measured variable $v$.

@@

```{r data-structure, fig.cap = "The data structure for exploring periodicities in data by including cyclic granularities in the tsibble structure with index, key and measured variables.", fig.pos="htb"}
include_graphics("Figs/data-struc-rev.png")
```

>>>>

\noindent All cyclic granularities can be expressed in terms of the index set, and hence, we introduce the data structure in Figure \@ref(fig:data-structure). This basic structure of a tsibble (index, key, measurements) is augmented by columns of cyclic granularities.The total number of cyclic granularities would be based on the number of linear granularities considered in the hierarchy table and presence of any aperiodic cyclic granularities, for example, if we have $n$ periodic linear granularities in the hierarchy table, $n(n-1)/2$ circular or quasi-circular cyclic granularities could be constructed. Let $N_C$ be the total number of contextual circular, quasi-circular and aperiodic cyclic granularities that could originate from $N_L$ periodic and aperiodic linear granularities. Any attempt to encode all or many of these cyclic granularities at the same time to develop insights on periodicity might fail or otherwise become too numerous for comprehensive human consumption. Instead, this big problem is broken down by focusing on pair of cyclic granularities ($C_i$, $C_j$) at a time for $i, j \in \{1, 2, \dots, N_C\}$. Data sets of the form <$C_i$, $C_j$, $v$> then forms the basis for exploration and analysis of the measured variable $v$.

@@

```{r data-structure, fig.cap = "The data structure for exploring periodicities in data by including cyclic granularities in the tsibble structure with index, key and measured variables.", fig.pos="htb"}
include_graphics("Figs/data-struc-diffcol.png")
```
